\chapter{Windows 10 Remote Desktop}
\label{ch_rdp}

The lab machines are accessible by windows 10 remote desktop. You will need to be on the campus virtual private network (VPN) first. The \url{https://uwaterloo.ca/information-systems-technology/services/virtual-private-network-vpn} gives detailed instructions on how to connect to the campus VPN. If you are in China, a special instruction can be found at \url{https://wiki.uwaterloo.ca/display/ISTKB/Accessing+Waterloo+learning+technologies+from+China+using+special+VPN}.

The Englab at \url{https://englab.uwaterloo.ca/} is the main gateway. Choose {\bf ECE $\rightarrow$ ece-rtos*} machines. Use remote desktop application on your computer to open up the downloaded file. For Windows 10 platform, when prompt for user name, input \verb+Nexus\userid+, where the \verb+userid+ is your quest ID. For Linux or MAC platforms, input \verb+Nexus+ in the domain field, input your quest ID in the username field. The password is your Quest password. Then you are connected to one of the lab machines that has the software and hardware installed for this lab.

Please be advised that if you are idle on a lab machine for an extended period of time, your session will automatically times out and your account will be locked from using this computer for a period of time. While your account is locked for a machine, you may still be able to login onto the machine. But most of the software installed on the machine will become inaccessible. 

Once you finish using the lab computer, remember to close all your programs and logout from the remote desktop session.
